---
title: "Presentation"
author: "Daniel Fridljand, Benedikt Lauer, Henning Stein, Niklas Wünstel"
date: "February 20, 2019"
output:
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("../R/Basis_expansion.R")
source("../R/Test.R")
source("../R/oop.R")
source("../R/Estimators.R")
source("../R/Classifier_funs.R")
source("../R/plot_functions.R")
source("../R/shinyplot.R")
set.seed(2)
height_B <- rnorm(115, mean = 30, sd = 4)
decibel_B <- rnorm(115, mean = 70, sd = 10)
classes_B <- rep("Barock", 115)

height_R <- rnorm(78, mean = 17, sd = 6)
decibel_R <- rnorm(78, mean = 102, sd = 7)
classes_R <- rep("Renaissance", 78)

height_C <- rnorm(96, mean = 42, sd = 7)
decibel_C <- rnorm(96, mean = 64, sd = 8)
classes_C <- rep("Classic", 96)

height <- c(height_B, height_R, height_C)
decibel <- c(decibel_B, decibel_R, decibel_C)
class <- c(classes_B, classes_R, classes_C)

Rockets <- data.frame(decibel = decibel, height = height, class = class)
set.seed(2)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets
1. Item 1
2. Item 2
    a. Item 2a
    b. Item 2b

- Bullet 1
    - Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
str(Rockets)
summary(Rockets)
```

## Creating a set

```{r Creating a set, results='hide', echo = TRUE}
Rocket_set <- 
  make_set(Rockets, 
           by = 'class', 
           title = "Rockets", 
           description = "Rockets with their flight heigth")
```

```{r creating the classfun, echo = TRUE}
func_example1 <- LDA(Rocket_set)[['name']]
```

```{r Creating a plot, results='hide', echo = TRUE}
exampleplot1 <- make_2D_plot(Rocket_set,
               func_example1,
               ppu = 1,
               project = FALSE)
```

## Plotting the test
```{r displaying plot}
exampleplot1
```